Nitric oxide feedback to ciliary photoreceptor cells gates a UV avoidance circuit

### 2023-06-13 Manuscript/Manuscript.Rmd
Ms: model section edit

To generate new insights from the model, we asked how the duration and intensity of UV stimulation influences signalling output, measured as the magnitude, duration and time to maximum of the NO-dependent Ca^2+^ signal in the cPRCs.
The model allowed us to test a large number of conditions that would not have been feasible in single-larva experiments.
We found that the onset, magnitude and duration of the NO-dependent signal scales with stimulus intensity and duration (Figure 6--figure supplement 2).
This suggests an integratory function of NO signalling that tunes circuit output to the strength of UV exposure.

>>>>

To generate new insights from the model, we asked how the duration and intensity of UV stimulation influences signalling output, measured as the magnitude (quantified as area under peak, AUP) of the NO-dependent Ca^2+^ signal in the cPRCs.
The model allowed us to systematically vary stimulus conditions that would not have been feasible in single-larva experiments.
We found that the magnitude of the NO-dependent signal scales with stimulus intensity and duration (Figure 7).
This suggests an integratory function of NO signalling that tunes circuit output to the strength of UV exposure.
